Paper 2, Econ 980x

### 2022-12-12 Paper2.Rmd
commit

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(ggplot2)
library(janitor)
library(ggthemes)
library(stargazer)
library(tinytex)
library(ipumsr)
library(dplyr)
library(haven)
library(survey)
library(spatstat)

@@

# education
newcsv1 <- newcsv %>%
  mutate(new_educ = ifelse(code_education <= 17, "<High School", ifelse(code_education >= 40, ">Four Year Degree", "High School Graduate")))
  newcsv1

@@

newcsv1

@@

stargazer(a, b, c, d, title="Various Models", align=TRUE, type = "text")
```

@@

newcsv1 %>%
  ggplot(mapping = aes(x = bls_leis)) +
  geom_histogram() +
  facet_wrap(~emp)

newcsv1 %>%
  group_by(emp, gender, new_educ, year) %>%
  summarize(median = median(bls_leis)) %>%
  ggplot(mapping = aes(x = year, y = median, group = new_educ, colour = new_educ)) +
  geom_line() +
  facet_wrap(~gender + emp) +
  labs(
  title = "Daily individual leisure minutes",
  y = "Daily Minutes",
  x = "Count",
  caption = "Data from ATUS",
)

@@

newcsv1 %>%
  filter(year > 2006) %>%
  filter(year < 2011) %>%
  group_by(emp, gender) %>%
  tally()

@@

newcsv1 %>%
  filter(year > 2006) %>%
  filter(year < 2011) %>%
  group_by(emp, year) %>%
  tally() %>%
  pivot_wider(names_from = year, values_from = n) %>%
  clean_names() %>%
  mutate(change_2008 = x2008-x2007) %>%
  mutate(change_2009 = x2009-x2008) %>%
  mutate(change_2010 = x2010-x2009) %>%
  select(1, 6:8)

@@

change <- newcsv1 %>%
  group_by(gender,  year, new_educ, child, marst_simple) %>%
  summarize(median(bls_leis)) %>%
  clean_names() %>%
  pivot_wider(values_from = median_bls_leis, names_from = year) %>%
  clean_names() %>%
  mutate(leisure_change = x2009 - x2007)

change11 <- newcsv1 %>%
  group_by(gender,  year, new_educ, child, marst_simple, emp) %>%
  summarize(median(bls_leis)) %>%
  clean_names() %>%
  pivot_wider(values_from = median_bls_leis, names_from = year) %>%
  clean_names() %>%
  mutate(leisure_change = x2009 - x2007)

change2 <- newcsv1 %>%
  group_by(gender, year) %>%
  summarize(median(bls_leis)) %>%
  clean_names() %>%
  pivot_wider(values_from = median_bls_leis, names_from = year) %>%
  clean_names() %>%
  mutate(leisure_change = x2009 - x2007)

change3 <- newcsv1 %>%
  group_by(gender,  year, new_educ, nchild, marst_simple) %>%
  summarize(median(bls_leis)) %>%
  clean_names() %>%
  pivot_wider(values_from = median_bls_leis, names_from = year) %>%
  clean_names() %>%
  mutate(leisure_change = x2009 - x2007)

change4 <- newcsv1 %>%
  group_by(gender,  year, new_educ, nchild, marst_simple) %>%
  summarize(mean(bls_leis)) %>%
  clean_names() %>%
  pivot_wider(values_from = mean_bls_leis, names_from = year) %>%
  clean_names() %>%
  mutate(leisure_change = x2009 - x2007)

change12 <- newcsv1 %>%
  group_by(gender,  year, emp) %>%
  summarize(median(bls_leis)) %>%
  clean_names() %>%
  pivot_wider(values_from = median_bls_leis, names_from = year) %>%
  clean_names() %>%
  mutate(leisure_change = x2009 - x2007)

@@

stargazer(delta, delta3, title="Models for Change in Leisure", align=TRUE, type = "text")

@@

summary(newcsv1)

time_model <- newcsv1 %>%
  mutate(year = as.character(year)) %>%
  lm(formula = bls_leis ~ gender + year + gender*year + age + race + new_educ )

summary(time_model)

# W employment
time_model1 <- newcsv1 %>%
  mutate(year = as.character(year)) %>%
  lm(formula = bls_leis ~ gender + year + gender*year + age + race + new_educ + emp)

summary(time_model1)

# W emp*gender
time_model2 <- newcsv1 %>%
  mutate(year = as.character(year)) %>%
  lm(formula = bls_leis ~ gender + year + gender*year + age + race + new_educ + emp*year)

summary(time_model2)

newcsv1

@@

```{r tables, results = "asis"}

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(ggplot2)
library(janitor)
library(ggthemes)
library(stargazer)
library(tinytex)
library(ipumsr)
library(dplyr)
library(haven)
library(survey)
library(spatstat)
library(kableExtra)
library(lfe)

@@

# education
newcsv1 <- newcsv %>%
  mutate(new_educ = ifelse(code_education <= 17, "<High School", ifelse(code_education >= 40, ">Four Year Degree", "High School Graduate")))

@@

@@

```{r table0, results = "asis"}
stargazer(a, b, c, d, title="Various Models", align=TRUE, type = "html")
```

@@

newcsv1 %>%
  ggplot(mapping = aes(x = bls_leis)) +
  geom_histogram() +
  facet_wrap(~emp) +
  labs(
  title = "Daily individual leisure minutes by employment type",
  y = "Count",
  x = "Daily Minutes",
  caption = "Data from ATUS",
)

newcsv1 %>%
  filter(year < 2020) %>%
  group_by(emp, gender, new_educ, year) %>%
  summarize(median = weighted.median(bls_leis, wt06)) %>%
  ggplot(mapping = aes(x = year, y = median, group = new_educ, colour = new_educ)) +
  geom_line() +
  facet_wrap(~gender + emp) +
  labs(
  title = "Weighted daily individual leisure minutes",
  y = "Daily Minutes",
  x = "Count",
  caption = "Data from ATUS",
)

newcsv1 %>%
  filter(year < 2020) %>%
  group_by(emp, gender, new_educ, year) %>%
  summarize(median = median(bls_leis)) %>%
  ggplot(mapping = aes(x = year, y = median, group = new_educ, colour = new_educ)) +
  geom_line() +
  facet_wrap(~gender + emp) +
  labs(
  title = "Daily individual leisure minutes",
  y = "Daily Minutes",
  x = "Count",
  caption = "Data from ATUS",
)

newcsv1 %>%
  filter(year > 2006) %>%
  filter(year < 2011) %>%
  group_by(emp, gender, new_educ, year) %>%
  summarize(median = weighted.median(bls_leis, wt06)) %>%
  ggplot(mapping = aes(x = year, y = median, group = new_educ, colour = new_educ)) +
  geom_line() +
  facet_wrap(~gender + emp) +
  labs(
  title = "Weighted daily individual leisure minutes",
  y = "Daily Minutes",
  x = "Count",
  caption = "Data from ATUS",
)

@@

count_table <- newcsv1 %>%
  filter(year > 2006) %>%
  filter(year < 2011) %>%
  group_by(emp, gender) %>%
  tally()

count_table2 <- newcsv1 %>%
  filter(year > 2006) %>%
  filter(year < 2011) %>%
  group_by(emp, gender, new_educ) %>%
  tally()

kable(count_table2) %>% kable_styling()
kable(count_table) %>% kable_styling()

@@

newcsv1 %>%
  filter(year > 2006) %>%
  filter(year < 2011) %>%
  group_by(emp, year) %>%
  tally() %>%
  pivot_wider(names_from = year, values_from = n) %>%
  clean_names() %>%
  mutate(change_2008 = x2008-x2007) %>%
  mutate(change_2009 = x2009-x2008) %>%
  mutate(change_2010 = x2010-x2009) %>%
  select(1, 6:8) %>%
  kbl() %>%
  kable_styling()

@@

change <- newcsv1 %>%
  filter(year<2020) %>%
  group_by(gender,  year, new_educ, child, marst_simple) %>%
  summarize(median_bls_leis = weighted.median(bls_leis, wt06)) %>%
  clean_names() %>%
  pivot_wider(values_from = median_bls_leis, names_from = year) %>%
  clean_names() %>%
  mutate(leisure_change = x2009 - x2007)

change11 <- newcsv1 %>%
  filter(year<2020) %>%
  group_by(gender,  year, new_educ, child, marst_simple, emp) %>%
   summarize(median_bls_leis = weighted.median(bls_leis, wt06)) %>%
  clean_names() %>%
  pivot_wider(values_from = median_bls_leis, names_from = year) %>%
  clean_names() %>%
  mutate(leisure_change = x2009 - x2007)

change2 <- newcsv1 %>%
  filter(year<2020) %>%
  group_by(gender, year) %>%
  summarize(median_bls_leis = weighted.median(bls_leis, wt06)) %>%
  clean_names() %>%
  pivot_wider(values_from = median_bls_leis, names_from = year) %>%
  clean_names() %>%
  mutate(leisure_change = x2009 - x2007)

change3 <- newcsv1 %>%
  filter(year<2020) %>%
  group_by(gender,  year, new_educ, nchild, marst_simple) %>%
   summarize(median_bls_leis = weighted.median(bls_leis, wt06)) %>%
  clean_names() %>%
  pivot_wider(values_from = median_bls_leis, names_from = year) %>%
  clean_names() %>%
  mutate(leisure_change = x2009 - x2007)

change4 <- newcsv1 %>%
  filter(year<2020) %>%
  group_by(gender,  year, new_educ, nchild, marst_simple) %>%
  summarize(mean(bls_leis)) %>%
  clean_names() %>%
  pivot_wider(values_from = mean_bls_leis, names_from = year) %>%
  clean_names() %>%
  mutate(leisure_change = x2009 - x2007)

change12 <- newcsv1 %>%
  filter(year<2020) %>%
  group_by(gender,  year, emp) %>%
   summarize(median_bls_leis = weighted.median(bls_leis, wt06)) %>%
  clean_names() %>%
  pivot_wider(values_from = median_bls_leis, names_from = year) %>%
  clean_names() %>%
  mutate(leisure_change = x2009 - x2007)

@@

```{r table1, , results = "asis"}
stargazer(delta, delta3, title="Models for Change in Leisure", align=TRUE, type = "html")

@@

# First Set

time_model <- newcsv1 %>%
  filter(year < 2020) %>%
  mutate(year = as.character(year)) %>%
  lm(formula = bls_leis ~ gender + year + gender*year + age + race + new_educ,weights = wt06 )

# W employment
time_model1 <- newcsv1 %>%
  filter(year < 2020) %>%
  mutate(year = as.character(year)) %>%
  lm(formula = bls_leis ~ gender + year + gender*year + age + race + new_educ + emp, weights = wt06)

# W emp*gender

time_model2 <- newcsv1 %>%
  filter(year < 2020) %>%
  mutate(year = as.character(year)) %>%
  lm(formula = bls_leis ~ gender + year + gender*year + age + race + new_educ + emp + emp*year, weights = wt06)

@@

```{r table2, results = "asis"}

@@

#stargazer(time_modela, time_model1a, time_model2a8, title="Models for Change in Leisure", align=TRUE, type = "html")
```

```{r}

newcsv1 %>%
  filter(year > 2006) %>%
  filter(year < 2009) %>%
  summarize(median_bls_leis_arts = weighted.median(bls_leis_arts, wt06),
            median_bls_leis_attend = weighted.median(bls_leis_attend, wt06),
            median_bls_leis_attsport = weighted.median(bls_leis_attsport, wt06),
            median_bls_leis_partsport = weighted.median(bls_leis_partsport, wt06),
            median_bls_leis_relax = weighted.median(bls_leis_relax, wt06),
            median_bls_leis_soc = weighted.median(bls_leis_soc, wt06),
            median_bls_leis_sport = weighted.median(bls_leis_sport, wt06),
            median_bls_leis_soccom = weighted.median(bls_leis_arts, wt06),
            median_bls_leis_travel = weighted.median(bls_leis_travel, wt06),
            median_bls_leis_tv = weighted.median(bls_leis_tv, wt06)) %>%
  pivot_longer(cols = everything(), names_to = "Activity", values_to = "Median Weighted Daily Minutes") %>%
  kbl() %>%
  kable_styling()

newcsv1 %>%
  filter(year > 2006) %>%
  filter(year < 2009) %>%
  summarize(mean_bls_leis_arts = weighted.mean(bls_leis_arts, wt06),
            mean_bls_leis_attend = weighted.mean(bls_leis_attend, wt06),
            mean_bls_leis_attsport = weighted.mean(bls_leis_attsport, wt06),
            mean_bls_leis_partsport = weighted.mean(bls_leis_partsport, wt06),
            mean_bls_leis_relax = weighted.mean(bls_leis_relax, wt06),
            mean_bls_leis_soc = weighted.mean(bls_leis_soc, wt06),
            mean_bls_leis_sport = weighted.mean(bls_leis_sport, wt06),
            mean_bls_leis_soccom = weighted.mean(bls_leis_arts, wt06),
            mean_bls_leis_travel = weighted.mean(bls_leis_travel, wt06),
            mean_bls_leis_tv = weighted.mean(bls_leis_tv, wt06)) %>%
  pivot_longer(cols = everything(), names_to = "Activity", values_to = "Mean Weighted Daily Minutes") %>%
  kbl() %>%
  kable_styling()

newcsv1 %>%
  filter(year > 2006) %>%
  filter(year < 2009) %>%
  group_by(gender) %>%
  summarize(median_bls_leis_arts = weighted.median(bls_leis_arts, wt06),
            median_bls_leis_attend = weighted.median(bls_leis_attend, wt06),
            median_bls_leis_attsport = weighted.median(bls_leis_attsport, wt06),
            median_bls_leis_partsport = weighted.median(bls_leis_partsport, wt06),
            median_bls_leis_relax = weighted.median(bls_leis_relax, wt06),
            median_bls_leis_soc = weighted.median(bls_leis_soc, wt06),
            median_bls_leis_sport = weighted.median(bls_leis_sport, wt06),
            median_bls_leis_soccom = weighted.median(bls_leis_arts, wt06),
            median_bls_leis_travel = weighted.median(bls_leis_travel, wt06),
            median_bls_leis_tv = weighted.median(bls_leis_tv, wt06)) %>%
  pivot_longer(!gender, names_to = "Activity", values_to = "Median Weighted Daily Minutes") %>%
  kbl() %>%
  kable_styling()

newcsv1 %>%
  filter(year > 2006) %>%
  filter(year < 2009) %>%
  group_by(emp, gender, new_educ, year) %>%
  summarize(median_bls_leis_arts = weighted.median(bls_leis_arts, wt06),
            median_bls_leis_attend = weighted.median(bls_leis_attend, wt06),
            median_bls_leis_attsport = weighted.median(bls_leis_attsport, wt06),
            median_bls_leis_partsport = weighted.median(bls_leis_partsport, wt06),
            median_bls_leis_relax = weighted.median(bls_leis_relax, wt06),
            median_bls_leis_soc = weighted.median(bls_leis_soc, wt06),
            median_bls_leis_sport = weighted.median(bls_leis_sport, wt06),
            median_bls_leis_soccom = weighted.median(bls_leis_arts, wt06),
            median_bls_leis_travel = weighted.median(bls_leis_travel, wt06),
            median_bls_leis_tv = weighted.median(bls_leis_tv, wt06)) %>%
  ggplot(mapping = aes(x = year, y = median, group = new_educ, colour = new_educ)) +
  geom_line() +
  facet_wrap(~gender + emp) +
  labs(
  title = "Daily individual leisure minutes",
  y = "Daily Minutes",
  x = "Count",
  caption = "Data from ATUS",
)

newcsv1 %>%
  filter(year > 2006) %>%
  filter(year < 2009) %>%
  group_by(emp, gender, new_educ, year) %>%
  summarize(median_bls_leis_arts = weighted.mean(bls_leis_arts, wt06),
            median_bls_leis_attend = weighted.mean(bls_leis_attend, wt06),
            median_bls_leis_attsport = weighted.mean(bls_leis_attsport, wt06),
            median_bls_leis_partsport = weighted.mean(bls_leis_partsport, wt06),
            median_bls_leis_relax = weighted.mean(bls_leis_relax, wt06),
            median_bls_leis_soc = weighted.mean(bls_leis_soc, wt06),
            median_bls_leis_sport = weighted.mean(bls_leis_sport, wt06),
            median_bls_leis_soccom = weighted.mean(bls_leis_arts, wt06),
            median_bls_leis_travel = weighted.mean(bls_leis_travel, wt06),
            median_bls_leis_tv = weighted.mean(bls_leis_tv, wt06))

# TV Mean by Group   
newcsv1 %>%
  filter(year > 2006) %>%
  filter(year < 2009) %>%
  group_by(emp, gender, new_educ, year) %>%
  summarize(mean_bls_leis_arts = weighted.mean(bls_leis_arts, wt06),
            mean_bls_leis_attend = weighted.mean(bls_leis_attend, wt06),
            mean_bls_leis_attsport = weighted.mean(bls_leis_attsport, wt06),
            mean_bls_leis_partsport = weighted.mean(bls_leis_partsport, wt06),
            mean_bls_leis_relax = weighted.mean(bls_leis_relax, wt06),
            mean_bls_leis_soc = weighted.mean(bls_leis_soc, wt06),
            mean_bls_leis_sport = weighted.mean(bls_leis_sport, wt06),
            mean_bls_leis_soccom = weighted.mean(bls_leis_arts, wt06),
            mean_bls_leis_travel = weighted.mean(bls_leis_travel, wt06),
            mean_bls_leis_tv = weighted.mean(bls_leis_tv, wt06)) %>%
  ggplot(mapping = aes(x = mean_bls_leis_tv, y = emp, colour = new_educ)) +
  geom_point() +
  facet_wrap(~ gender + new_educ) +
    labs(
  title = "Average minutes individuals spend on watching TV",
  y = "Employment Status",
  x = "Daily Minutes",
  caption = "Data from ATUS",
)

newcsv1 %>%
  filter(year > 2006) %>%
  filter(year < 2009) %>%
  group_by(emp, gender, new_educ, year) %>%
  summarize(mean_bls_leis_arts = weighted.mean(bls_leis_arts, wt06),
            mean_bls_leis_attend = weighted.mean(bls_leis_attend, wt06),
            mean_bls_leis_attsport = weighted.mean(bls_leis_attsport, wt06),
            mean_bls_leis_partsport = weighted.mean(bls_leis_partsport, wt06),
            mean_bls_leis_relax = weighted.mean(bls_leis_relax, wt06),
            mean_bls_leis_soc = weighted.mean(bls_leis_soc, wt06),
            mean_bls_leis_sport = weighted.mean(bls_leis_sport, wt06),
            mean_bls_leis_soccom = weighted.mean(bls_leis_arts, wt06),
            mean_bls_leis_travel = weighted.mean(bls_leis_travel, wt06),
            mean_bls_leis_tv = weighted.mean(bls_leis_tv, wt06)) %>%
  ggplot(mapping = aes(x = mean_bls_leis_relax, y = emp, colour = new_educ)) +
  geom_point() +
  facet_wrap(~ gender + new_educ) +
  labs(
  title = "Average minutes individuals spend on relaxation",
  y = "Employment Status",
  x = "Daily Minutes",
  caption = "Data from ATUS",
)

newcsv1 %>%
  filter(year > 2006) %>%
  filter(year < 2009) %>%
  group_by(emp, gender, new_educ, year) %>%
  summarize(mean_bls_leis_arts = weighted.mean(bls_leis_arts, wt06),
            mean_bls_leis_attend = weighted.mean(bls_leis_attend, wt06),
            mean_bls_leis_attsport = weighted.mean(bls_leis_attsport, wt06),
            mean_bls_leis_partsport = weighted.mean(bls_leis_partsport, wt06),
            mean_bls_leis_relax = weighted.mean(bls_leis_relax, wt06),
            mean_bls_leis_soc = weighted.mean(bls_leis_soc, wt06),
            mean_bls_leis_sport = weighted.mean(bls_leis_sport, wt06),
            mean_bls_leis_soccom = weighted.mean(bls_leis_arts, wt06),
            mean_bls_leis_travel = weighted.mean(bls_leis_travel, wt06),
            mean_bls_leis_tv = weighted.mean(bls_leis_tv, wt06)) %>%
  ggplot(mapping = aes(x = mean_bls_leis_soc, y = emp, colour = new_educ)) +
  geom_point() +
  facet_wrap(~ gender + new_educ) +
  labs(
  title = "Average minutes individuals spend on socializing",
  y = "Employment Status",
  x = "Daily Minutes",
  caption = "Data from ATUS",
)
